% THIS IS SIGPROC-SP.TEX - VERSION 3.1
% WORKS WITH V3.2SP OF ACM_PROC_ARTICLE-SP.CLS
% APRIL 2009
%
% It is an example file showing how to use the 'acm_proc_article-sp.cls' V3.2SP
% LaTeX2e document class file for Conference Proceedings submissions.
% ----------------------------------------------------------------------------------------------------------------
% This .tex file (and associated .cls V3.2SP) *DOES NOT* produce:
%       1) The Permission Statement
%       2) The Conference (location) Info information
%       3) The Copyright Line with ACM data
%       4) Page numbering
% ---------------------------------------------------------------------------------------------------------------
% It is an example which *does* use the .bib file (from which the .bbl file
% is produced).
% REMEMBER HOWEVER: After having produced the .bbl file,
% and prior to final submission,
% you need to 'insert'  your .bbl file into your source .tex file so as to provide
% ONE 'self-contained' source file.
%
% Questions regarding SIGS should be sent to
% Adrienne Griscti ---> griscti@acm.org
%
% Questions/suggestions regarding the guidelines, .tex and .cls files, etc. to
% Gerald Murray ---> murray@hq.acm.org
%
% For tracking purposes - this is V3.1SP - APRIL 2009

%%\documentclass{sig-alternate}
%%hp cr: using www2012-accepted
\documentclass{www2012-accepted}
%\usepackage{cite}
\usepackage{url}
\usepackage{hyperref}
%\usepackage[table]{xcolor} 
\usepackage{times}
\usepackage{color}
%\usepackage{multirow} %mk
\usepackage{verbatim}

\usepackage{multirow}
\begin{document}
\clubpenalty=10000 
\widowpenalty = 10000
\newcommand{\xhdr}[1]{{\vspace{6pt}\noindent\textbf{\textit{#1}}}}

\newcommand{\soic}{\affaddr{School of Informatics \& Computing}\\ 
\affaddr{Indiana University}\\
\affaddr{Bloomington, IN}\\}

\title{TBD}
%{Mining Photo-sharing Websites to Study\\ Ecological Phenomena}

\begin{comment}

\numberofauthors{4} %  in this sample file, there are a *total*
% of EIGHT authors. SIX appear on the 'first-page' (for formatting
% reasons) and the remaining two appear in the \additionalauthors section.
%


\author{
% You can go ahead and credit any number of authors here,
% e.g. one 'row of three' or two rows (consisting of one row of three
% and a second row of one, two or three).
%
% The command \alignauthor (no curly braces needed) should
% precede each author name, affiliation/snail-mail address and
% e-mail address. Additionally, tag each line of
% affiliation/address with \affaddr, and tag the
% e-mail address with \email.
%
% 1st. author
\alignauthor
%Anonymous CIKM submission \\
 Haipeng Zhang\\
 \soic
 \email{zhanhaip@indiana.edu}
 % 2nd. author
 \alignauthor
 Mohammed Korayem\\
 \soic
 \email{mkorayem@indiana.edu}
 % 3rd. author
 \alignauthor 
 David J. Crandall \\
 \soic
 \email{djcran@indiana.edu}
 \and
 \alignauthor
 Gretchen LeBuhn \\
 \affaddr{Department of Biology} \\
 \affaddr{University of California} \\
 \affaddr{San Francisco, CA} 
 \email{lebuhn@sfsu.edu}
}

% There's nothing stopping you putting the seventh, eighth, etc.
% author on the opening page (as the 'third row') but we ask,
% for aesthetic reasons that you place these 'additional authors'
% in the \additional authors block, viz.
%\additionalauthors{Additional authors: John Smith (The Th{\o}rv{\"a}ld Group,
%email: {\texttt{jsmith@affiliation.org}}) and Julius P.~Kumquat
%(The Kumquat Consortium, email: {\texttt{jpkumquat@consortium.net}}).}
%\date{30 July 1999}
% Just remember to make sure that the TOTAL number of authors
% is the number that will appear on the first page PLUS the
% number that will appear in the \additionalauthors section.
\end{comment}

\begin{comment}
\end{comment}
\maketitle
\begin{abstract}
The popularity of social media websites like Flickr
and Twitter has created enormous collections of user-generated content
online. Latent in these content collections are observations of the
world: each photo is a visual snapshot of what the world looked like
at a particular point in time and space, for example, while each tweet
is a textual expression of the state of a person and his or her
environment. Aggregating these observations across millions
of social sharing users could lead to new techniques for large-scale
monitoring of the state of the world and how it is changing over
time. In this paper we step towards that goal, showing that by
analyzing the tags and image features of geo-tagged, time-stamped
photos we can measure and quantify the occurrence of ecological
phenomena including ground snow cover, snow fall and vegetation
density.  We compare several techniques for dealing with the large
degree of noise in the dataset, and show how machine learning can be
used to reduce errors caused by misleading tags and ambiguous visual
content. We evaluate the accuracy of these techniques by comparing to
ground truth data collected both by surface stations and by
Earth-observing satellites. Besides the immediate application to
ecology, our study gives insight into how to accurately crowd-source                                                                                                                           
other types of information from large, noisy social sharing datasets.
\end{abstract}

%% A category with the (minimum) three required fields
%\category{H.2.8}{Database Management}{Database Applications}[Data
%Mining, Image Databases, Spatial Databases and GIS]
%\category{I.4.8}{Image Processing and Computer Vision}{Scene Analysis}
%
%\terms{Measurement, Theory}
%
%\keywords{Data mining, social media, photo collections, crowd-sourcing, ecology} % NOT required for Proceedings

\newcommand{\leaveout}[1]{}

\newenvironment{packed_itemize}{
\begin{itemize}
  \setlength{\itemsep}{0pt}
  \setlength{\parskip}{0pt}
  \setlength{\parsep}{0pt}
\vspace{-4pt}
}{\end{itemize}}

\vspace{12pt}
\input{intro}

\input{relatedwork}
\input{methods}
\input{results}
\newpage
\input{conclusion}

%%hp cr: added acknowledgments

\input{ack}

\begin{comment}

%
% The following two commands are all you need in the
% initial runs of your .tex file to
% produce the bibliography for the citations in your paper.
\bibliographystyle{abbrv}
{\small
\begin{thebibliography}{10}
\vspace{5pt}
\bibitem{ghcn}
http://www.ncdc.noaa.gov/oa/climate/ghcn-daily/.

\bibitem{greatsunflower}
The great sunflower project.
\newblock http://www.greatsunflower.org.

\bibitem{lostladybug}
Lost ladybug project.
\newblock http://www.lostladybug.org.

\bibitem{anagnostpopoulos08}
A.~Anagnostopoulos, R.~Kumar, and M.~Mahdian.
\newblock Influence and correlation in social networks.
\newblock In {\em KDD}, 2008.

\bibitem{bollen11twitter}
J.~Bollen, H.~Mao, and X.-J. Zeng.
\newblock Twitter mood predicts the stock market.
\newblock {\em Journal of Computational Science}, 2(1):1--8, 2011.

\bibitem{brockmann06}
D.~Brockmann, L.~Hufnagel, and T.~Geisel.
\newblock The scaling laws of human travel.
\newblock {\em Nature}, 439:462--465, 2006.

\bibitem{CC01a}
C.-C. Chang and C.-J. Lin.
\newblock {LIBSVM}: A library for support vector machines.
\newblock {\em ACM Trans. on Intelligent Systems and Technology}, 2:1--27,
  2011.

\bibitem{feedback08kdd}
D.~Crandall, D.~Cosley, D.~Huttenlocher, J.~Kleinberg, and S.~Suri.
\newblock Feedback effects between similarity and social influence in online
  communities.
\newblock In {\em KDD}, 2008.

\bibitem{delongueville09}
B.~De~Longueville, R.~S. Smith, and G.~Luraschi.
\newblock "{OMG}, from here, i can see the flames!".
\newblock In {\em Proc. Intl. Workshop on Location Based Social Networks},
  pages 73--80, 2009.

\bibitem{Fan2008}
R.-E. Fan, K.-W. Chang, C.-J. Hsieh, X.-R. Wang, and C.-J. Lin.
\newblock Liblinear: a library for large linear classification.
\newblock {\em Journal of Machine Learning Research}, 9:1871--1874, 2008.

\bibitem{ginsberg09flu}
J.~Ginsberg, M.~Mohebbi, R.~Patel, L.~Brammer, M.~Smolinski, and L.~Brilliant.
\newblock Detecting influenza epidemics using search engine query data.
\newblock {\em Nature}, 457:1012--1014, 2009.

\bibitem{modissnow}
D.~K. Hall, G.~A. Riggs, and V.~V. Salomonson.
\newblock {MODIS/Terra Snow Cover Daily L3 Global 0.05Deg CMG V004}.
\newblock Boulder, CO, USA: National Snow and Ice Data Center, 2011, updated
  daily.

\bibitem{hall2009weka}
M.~Hall, E.~Frank, G.~Holmes, B.~Pfahringer, P.~Reutemann, and I.~Witten.
\newblock The weka data mining software: an update.
\newblock {\em ACM SIGKDD Explorations Newsletter}, 11(1):10--18, 2009.

\bibitem{hays}
J.~Hays and A.~A. Efros.
\newblock {IM2GPS}: Estimating geographic information from a single image.
\newblock In {\em CVPR}, 2008.

\bibitem{lab}
R.~Hunt.
\newblock {\em Measuring Color}.
\newblock London: Fountain Press, 1998.

\bibitem{jin10prediction}
X.~Jin, A.~Gallagher, L.~Cao, J.~Luo, and J.~Han.
\newblock The wisdom of social multimedia: Using {F}lickr for prediction and
  forecast.
\newblock In {\em ACM Multimedia}, 2010.

\bibitem{john1995estimating}
G.~John and P.~Langley.
\newblock Estimating continuous distributions in bayesian classifiers.
\newblock In {\em Proc. Uncertainty in AI}, 1995.

\bibitem{Kremerskothen11}
K.~Kremerskothen.
\newblock http://blog.flickr.net/en/2011/08/04/6000000000/

\bibitem{modisveg}
{Land Processes Distributed Active Archive Center}.
\newblock {MODIS/Terra Vegetation Indices 16-Day L3 Global 0.05Deg CMG V005}.
\newblock Sioux Falls, SD: U.S. Geological Survey., 2011.

\bibitem{lazer09}
D.~{Lazer et al}.
\newblock Life in the network: the coming age of computational social science.
\newblock {\em Science}, 323(5915):721--723, 2009.

\bibitem{libennowell08}
D.~Liben-Nowell and J.~Kleinberg.
\newblock Tracing information flow on a global scale using internet
  chain-letter data.
\newblock {\em PNAS}, 12(105):4633--4638, 2008.

\bibitem{oconnor10mood}
B.~O'Connor, R.~Balasubramanyan, B.~Routedge, and N.~Smith.
\newblock From tweets to polls: Linking text sentiment to public opinion time
  series.
\newblock In {\em ICWSM}, 2010.

\bibitem{ipcc2007climate}
M.~L. Parry, O.~F. Canziani, J.~P. Palutikof, P.~J. van~der Linden, and C.~E.
  Hanson.
\newblock {\em IPCC, 2007: Climate Change 2007: Impacts, Adaptation, and
  Vulnerability}.
\newblock Cambridge University Press, 2007.

\bibitem{singh10socialpixels}
V.~K. Singh, M.~Gao, and R.~Jain.
\newblock Social pixels: genesis and evaluation.
\newblock In {\em ACM Multimedia}, 2010.

\bibitem{squires5}
M.~Squires and J.~Lawrimore.
\newblock Development of an operational northeast snowfall impact scale.
\newblock Technical report, NOAA National Climatic Data Center, 2006.

\bibitem{su2008discriminative}
J.~Su, H.~Zhang, C.~Ling, and S.~Matwin.
\newblock Discriminative parameter learning for bayesian networks.
\newblock In {\em ICML}, 2008.

\bibitem{szeliski}
R.~Szeliski.
\newblock {\em Computer Vision: Algorithms and Applications}.
\newblock Springer, 2010.

\bibitem{gist}
A.~Torralba.
\newblock Contextual priming for object detection.
\newblock {\em International Journal of Computer Vision}, 53(2):161--191, 2003.

\bibitem{auc}
I.~Vergara, T.~Norambuena, E.~Ferrada, A.~Slater, and F.~Melo.
\newblock {StAR}: a simple tool for the statistical comparison of {ROC} curves.
\newblock {\em BMC Bioinformatics}, 9(1):265, 2008.

\end{thebibliography}

}
\end{comment}
% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
%APPENDICES are optional
%\balancecolumns

% That's all folks!
\end{document}

